\documentclass[a4paper, 12pt]{article}

\usepackage[latin1]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}


\title{English: world of work}
\author{Guillaume Leroi}

\begin{document}
\maketitle

\section{My first internship}

My first job was in a little enterprise, based in the suburbs of
Paris. I was doing software development for their customers, and
sometimes for the enterprise itself. For some reasons, my supervisor
could not be present often enough. So I had to work alone and find
solutions by my self.

I had to do very different kinds of things which were not easy for the
beginner I was. I had to develop for example a instant messaging web
client without knowledge on the protocol and used web
technologies.

Some part of my work involved Romanians developers with which I had to
discuss and work as a team through Internet. Sometimes I was alone in
the company, so I had to answer to phone calls and do a kind of
secretary job.

This was a strange experience in the world of work, getting my first
glimpse of life in an company: the joy of doing something useful, the
strain between people sometimes. At least I discover that being
developer could be a good first job, but it can be my work for all my
life.

\section{Trekking through Auvergne's volcanos}

I always loved trekking. Walking through the nature with no one around
except a few friends. Generally, I trek with my cousin and some
friends, and we have two particularities: we know how to read a map
very well and we have some sense of planning, but we have no luck. So
regularly we sleep in a field and we wash ourselves, when possible, in
a river or in fountain.

I'm remenber a trekking's week when we we have no where to sleep and
wash ourselves for four days. we had too impose
rationing on food and water. But even if it was hard, I still have a
good souvenir of the trip.


\end{document}
